\cvsection{Experience}
\begin{cventries}
  \cventry
    {Senior Software Engineer}
    {Walmart Labs, India}
    {Bangalore, Karnataka}
    {Aug. 2018 - Present}
    {
      \begin{cvitems}
        \item {Developed Universal Fitment Widget for Search and Item Page.}
        \item {Site Speed Discovery and Improved cATF/ TTI on Search and Category Pages.}
        \item {Presented 2 talks on JavaScript and ReactJs wherein there were close to 120 folks who attended the event.}
      \end{cvitems}
    }
  \cventry
    {Full Stack Developer}
    {Appsfly.io (Aqui-hired to Walmart Labs)}
    {Bangalore, Karnataka}
    {Jan. 2017 - Aug. 2018}
    {
      \begin{cvitems}
        \item {First employee on the engineering team. Helped the company to scale the platform.}
        \item {Design \& Implemented a high availability, distributed system to run microapps using Socket.io, Kafka and Zookeeper.}
        \item {Design \& implemented the web sdk for web affiliation and IDE for the development of micro modules.}
        \item {Setup private VPC, secure configuration which has the auto-scale capability.}
        \item {Setup the whole environment for PCI Certification.}
        \item {Provided training sessions about Continuous Integration with Docker for a group of Software Engineers.}
      \end{cvitems}
    }
  \cventry
    {Lead Microservices}
    {Xoxoday (Nreach Online Services Pvt. Ltd.)}
    {Bangalore, Karnataka}
    {Aug. 2016 - Nov. 2016}
    {
      \begin{cvitems}
        \item {Design \& Developed micro services for multiple resouces available in the organization for cross communication.}
      \end{cvitems}
    }
  \cventry
    {Technology Lead}
    {Prozo (Edu4share Pvt. Ltd.)}
    {Delhi, New Delhi}
    {Jan. 2015 - Aug. 2016}
    {
      \begin{cvitems}
        \item {Early member of the team to take the system in production.}
        \item {Developed features and components for Prozo e-commerce and mobile app, to serve fast pages to more than 2 million unique visitors per year.}
        \item {Worked closely with sales \& marketing team for technology requirements and implementation.}
      \end{cvitems}
    }
  \cventry
    {Co Founder}
    {Avasyu (Ideal Nodes)}
    {Delhi, New Delhi}
    {Dec. 2013 - Jan. 2015}
    {
      \begin{cvitems}
        \item {Developed the backend of cloud-based school management system.}
        \item {Managed server setup, configuration and deployment.}
        \item {Managed other developers, pitching to clients and other tasks associated with running a business.}
      \end{cvitems}
    }
\end{cventries}
